%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins


\name{Emily R. Creager} 
\address{(520) 314 - 6680 \hfill EmilyRCreager.com} 
\vspace{0pt}
\address{EmilyRCreager@protonmail.com \hfill linkedin.com/in/EmilyRCreager}
\vspace{0pt}

\begin{document}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, SQL, JavaScript, HTML, CSS, Microsoft SQL Server, C \\ 
Tools & Snowflake, BigQuery, Postman, Git, JIRA, Docker, Google Cloud Platform (GCP), \\
 & Looker, Tableau, Spotfire, JupyterLab, Selenium IDE, Katalon Studio, Excel \\
Libraries & pandas, numpy, scikit-learn, pytorch, matplotlib, plotly, seaborn, openpyxl, scipy,  \\
 & statsmodels, multiprocessing, selenium, scrapy, requests, beautifulsoup, sendgrid
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection} {Senior Data Scientist,} {11/2023 - Present} {Pinecone Data (Freelance)} 
\item Train and optimize machine learning models to enhance prediction accuracy.
\item Refine ML pipelines in GCP to improve data processing efficiency and resolve logical errors.
\item Engineer robust data pipelines for data cleaning, preprocessing, and statistical analysis.
\item Create and present meaningful data visualizations to identify relationships between variables.
\item Apply feature engineering techniques to improve model robustness and accuracy.
\end{rSubsection}

\begin{rSubsection} {Senior Data Scientist,} {01/2018 - 08/2023} {Blue Triangle Technologies}
\item Led a project to select the optimal machine learning model for a large time-series dataset.
\item Transformed unstructured and disparate datasets into actionable and informative visualizations.
\item Developed Python scripts to identify unauthorized words, GDPR/CCPA compliance, and CSPs. 
\item Manipulated and analyzed large datasets to improve website performance and increase revenue. 
\item Created stable, reliable test cases across 75+ domains to identify performance bottlenecks. 
\item Developed lightweight JavaScript code to customize and improve data collection.
\item Mentored internal \& external teams on automation, website performance, and API integrations.
\end{rSubsection}

\begin{rSubsection}{Implementation Manager \& Data Analyst,}  {07/2016 - 05/2017} {Solium Capital}
\item Created and maintained SQL scripts for 22+ databases to ensure reliable data processing. 
\item Conducted data validation during ETL workflows to identify and resolve logical inconsistencies.
\item Managed 16+ projects with timely delivery and maintaining strong client communication.
\item Documented key project milestones and procedures in JIRA and Confluence.
%  \item Provided training and technical support for clients.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Research Assistant,} {05/2014 - 05/2016}{Accelerator Mass Spectrometry Laboratory}
\item Designed and built a high-precision gas ionization detector integrated with a solid state detector. 
\item Modeled ion interactions and simulated electric fields within the detector using MATLAB. 
\item Fabricated silicon nitride foils using UV lithography and plasma etching. 
%  \item Determined detector specifics by modeling ion interaction. 
\end{rSubsection}

\begin{rSubsection} {Vice President \& Team Lead,} {08/2013 - 12/2014} {Women in Science \& Engineering} 
\item  Promoted to Vice President for consistently demonstrating leadership and outstanding teamwork. 
\item  Led a multidisciplinary team, overseeing conflict resolution and fostering strong relationships.
\item  Served on the Executive Council to manage projects and drive intern professional development. 
\item Implemented experiential curriculum at conferences, mentoring programs, and expositions. 
\end{rSubsection}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	{\bf University of Arizona} \\ 
	{Bachelor of Science, {\em Physics}}\\
\end{rSection}
\end{document}
